Self-interacting dark matter model without dark energy in cosmology

### 2025-02-11 article/article.tex
theoretical solution?

   However, the Eq.(\ref{eq:8}) just have a singularity when $z\to\infty$, so the IDM
   model can not give a constraint to the $r_{\text{d}}$ and we just try to use the cross
   parameter $r_{\text{d}}h$ to give the constraints.

@@

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{qso_fx_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{qso_fx_2.pdf}
      }
      \caption{The constraint result from the quasar data}
   \end{figure}

>>>>

   However, the Eq.(\ref{eq:8}) just have a singularity when $t\to 0$ as $z\to\infty$,
   so the IDM model cannot give a constraint to the $r_{\text{d}}$ and we just try to use the cross
   parameter $r_{\text{d}}h$ to give the constraints.

@@
